How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-23 tse-paper/content.tex
Add text

%todo: fill-in number
Wtih these X remaining articles, we followed a limited backward
snowball sampling for articles referenced in the paragraphs that
mention the technique. Having added these papers to our literature
set, we performed a full forward-snowball sampling for all papers in
the set.

>>>>

%todo: fill-in number
Wtih these X remaining articles, we followed a backward snowball
sampling for other related work referenced in the paragraphs that
mention the technique. This added four papers (five before duplicate
elimination) to our literature set.
